Competing Bandits: The Perils of Exploration under Competition

### 2018-08-31 paper/content/introduction.tex
comment

Our findings on temporary monopoly shed light on the ``first-mover advantage" phenomenon in the digital economy. In this scenario, the incumbent firm enjoys both a ``data advantage" and a ``reputational advantage". We further investigate which of the two is a stronger barrier to entry. We find that both are strong barriers on its own: removing either one substantially helps the late entrant. Further, the data advantage tends to be a stronger barrier when the incumbent commits to a more advanced bandit algorithm.

>>>>

Our findings on temporary monopoly shed light on the ``first-mover advantage" phenomenon in the digital economy. In this scenario, the incumbent firm enjoys both a ``data advantage" and a ``reputational advantage". We further investigate which of the two is a stronger barrier to entry.\swcomment{so which of the two?} We find that both are strong barriers on its own: removing either one substantially helps the late entrant. Further, the data advantage tends to be a stronger barrier when the incumbent commits to a more advanced bandit algorithm.
